Carbonate chemistry at Ny-Ålesund

### 2022-08-04 awipev-CO2.Rmd
Saly_fb_mix now used, finalized ts plot

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_fb_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
  dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyLegend(show = "follow")   %>%
  dyAxis("y", valueRange = c(30, 37)) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_fb_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") &
        sal_fb_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_fb_mix < 34 ~ NA_real_,
      TRUE ~ sal_fb_mix
    )
  )
```

### **Depth profile**

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

@@

### **Comparison salinity FerryBox vs Salinity CTD REMOS 10 m** 
```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# REVIEW OK?
reg <- ggreg(
  xdata = d_all$sal_insitu_ctd_10m,
  ydata = d_all$sal_fb_mix,
  type = "MA",
  plot = TRUE,
  title = "Comparison salinity",
  #subtitle = "",
  xlab = "Salinity CTD REMOS 10 m",
  ylab = "Salinity FerryBox",
  proplot = TRUE,
  ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

Comparaison is done here with **corrected pHs** (**seaFET**, **durafet**
and **calculated** (from AT/CT)) and normalized at 4°C with a total
alkalinity of `r mean(d_all$at, na.rm = TRUE)` µmoles kg-1 (mean data).
For information, mean temperatures in Ferrybox and *in situ* are
repectively 3.5°C and 2.5°C.

@@

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = size_labs)

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
  Mytheme(size_labs = size_labs)

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="pCO2 at in situ temperature (measured in blue; calculated from CT and AT in red)",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = size_labs)

# SEAFET pH
ts_pH <- d_all %>% 
  dplyr::filter(depth > 8) %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="In situ pH below 8 m at in situ temperature (seaFET in blue; spectrophotometric in red)", x = "", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm'))

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="Total alkalinity (calculated from salinity in blue; discrete measurements in red)", x="", y="AT (umol/kg)") +
  Mytheme(size_labs = size_labs)

# Combine plots
g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
rm(list = ls(pattern = "ts_")) #delete big ggplot objects
gc() #garbage collection

#save_plot(filename = "figures/time_series.png", plot = g)
#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
```

@@

```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
size_point <- 0.5 # size of data points
alpha <- 1 #transparency
d_bp <- d_all %>% # just for this chunk
  dplyr::select(datetime, sal_fb, temp_insitu_11m, pco2_fb, pHint_tot_sf, at_calc)

# Quantiles table
Salinity <- round(quantile(d_bp$sal_fb, na.rm =TRUE), digits=1)
Temperature <- round(quantile(d_bp$temp_insitu_11m, na.rm =TRUE), digits=1)
pco2 <- round(quantile(d_bp$pco2_fb, na.rm =TRUE), digits=1)
pH <- round(quantile(d_bp$pHint_tot_sf, na.rm =TRUE), digits=3)
AT <- round(quantile(d_bp$at_calc, na.rm =TRUE), digits=1)
tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pco2, pH, AT)) %>%
  #rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
  dplyr::select(Variable, everything())
kable(tab_quartiles, caption = "Key quantiles") %>%
  kable_styling(full_width= FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# detection of extremes
# calculate 1st and 9th deciles 
dec_sal_fb <- quantile(d_bp$sal_fb, na.rm =TRUE, probs = c(0.1, 0.9))
dec_temp_insitu_11m <- quantile(d_bp$temp_insitu_11m, na.rm =TRUE, probs = c(0.1, 0.9))
dec_pco2_fb <- quantile(d_bp$pco2_fb, na.rm =TRUE, probs = c(0.1, 0.9))
dec_pHint_tot_sf <- quantile(d_bp$pHint_tot_sf, na.rm =TRUE, probs = c(0.1, 0.9))
dec_at_calc <- quantile(d_bp$at_calc, na.rm =TRUE, probs = c(0.1, 0.9))

# identify extremes
d_bp <- d_bp %>% 
  dplyr::mutate(ext_sal_fb = ifelse(sal_fb < dec_sal_fb[1] |
                                            sal_fb > dec_sal_fb[2], sal_fb, NA),
                ext_temp_insitu_11m = ifelse(temp_insitu_11m < dec_temp_insitu_11m[1] |
                                            temp_insitu_11m > dec_temp_insitu_11m[2],
                                            temp_insitu_11m, NA),
                ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                                            pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
                ext_pHint_tot_sf = ifelse(pHint_tot_sf < dec_pHint_tot_sf[1] |
                                            pHint_tot_sf > dec_pHint_tot_sf[2], pHint_tot_sf, NA),
                ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                                            at_calc > dec_at_calc[2], at_calc, NA))
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(y = "Salinity", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(y = "Temperature", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(y = "Total alkalinity", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
# Combine plots
g <- ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/ts_boxplots.png", plot = g)
rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
gc() #garbage collection
```

>>>>

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_fb_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (FerryBox and mix)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
  dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyLegend(show = "follow")   %>%
  dyAxis("y", valueRange = c(30, 37)) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_fb_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") &
        sal_fb_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_fb_mix < 34 ~ NA_real_,
      TRUE ~ sal_fb_mix
    )
  )
```

### **Depth profile**
This is done later.

```{r Sal profile, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

@@

### **Comparison salinity FerryBox vs Salinity CTD REMOS 10 m** 
```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# REVIEW OK?
reg <- ggreg(
  xdata = d_all$sal_insitu_ctd_10m,
  ydata = d_all$sal_fb,
  type = "MA",
  plot = TRUE,
  title = "Comparison salinity",
  #subtitle = "",
  xlab = "Salinity CTD REMOS 10 m",
  ylab = "Salinity FerryBox",
  proplot = TRUE,
  ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

Comparaison is done here with **corrected pHs** (**seaFET**, **durafet**
and **calculated** (from AT/CT)) and normalized at 4°C with a total
alkalinity of `r mean(d_all$at, na.rm = TRUE)` µmoles kg-1 (mean data).
For information, mean temperatures in Ferrybox and *in situ* are
respectively 3.5°C and 2.5°C.

@@

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="Salinity (below 8 m)",x="", y="Salinity") +
  Mytheme(size_labs = size_labs)

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="In situ temperature (11 m)",x="", y="Temperature (°C)") +
  Mytheme(size_labs = size_labs)

@@

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")),
       subtitle = "measured in blue; calculated from CT and AT in red",
       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
  Mytheme(size_labs = size_labs)

# SEAFET pH
ts_pH <- d_all %>% 
  dplyr::filter(depth > 8) %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="In situ pH below 8 m at in situ temperature", 
       subtitle = "seaFET in blue; spectrophotometric in red",
       x = "", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm'))

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
  labs(title="Total alkalinity", 
       subtitle = "calculated from salinity in blue; discrete measurements in red",
       x="", y=TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$")) +
  Mytheme(size_labs = size_labs)

# Combine plots
g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
#rm(list = ls(pattern = "ts_")) #delete big ggplot objects
#gc() #garbage collection
```

@@

```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
size_point <- 0.5 # size of data points
alpha <- 1 #transparency
d_bp <- d_all %>% # just for this chunk
  dplyr::select(datetime, sal_fb_mix, temp_insitu_11m, pco2_fb, pHint_tot_sf, at_calc)

# Quantiles table
Salinity <- round(quantile(d_bp$sal_fb_mix, na.rm =TRUE), digits=1)
Temperature <- round(quantile(d_bp$temp_insitu_11m, na.rm =TRUE), digits=1)
pco2 <- round(quantile(d_bp$pco2_fb, na.rm =TRUE), digits=1)
pH <- round(quantile(d_bp$pHint_tot_sf, na.rm =TRUE), digits=3)
AT <- round(quantile(d_bp$at_calc, na.rm =TRUE), digits=1)
tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pco2, pH, AT)) %>%
  #rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
  dplyr::select(Variable, everything())
kable(tab_quartiles, caption = "Key quantiles") %>%
  kable_styling(full_width= FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# detection of extremes
# calculate 1st and 9th deciles 
dec_sal_fb_mix <- quantile(d_bp$sal_fb_mix, na.rm =TRUE, probs = c(0.1, 0.9))
dec_temp_insitu_11m <- quantile(d_bp$temp_insitu_11m, na.rm =TRUE, probs = c(0.1, 0.9))
dec_pco2_fb <- quantile(d_bp$pco2_fb, na.rm =TRUE, probs = c(0.1, 0.9))
dec_pHint_tot_sf <- quantile(d_bp$pHint_tot_sf, na.rm =TRUE, probs = c(0.1, 0.9))
dec_at_calc <- quantile(d_bp$at_calc, na.rm =TRUE, probs = c(0.1, 0.9))

# identify extremes
d_bp <- d_bp %>%
  dplyr::mutate(
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
  )
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="Salinity (< 8 m)", y = "Salinity", x=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="In situ temperature (11 m)", y = "Temperature (°C)", x=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")), y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="In situ pH below 8 m at in situ temperature", y = expression(paste(pH[T])), x=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="Total alkalinity calculated from salinity", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank(),
        aspect.ratio=0.5)
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/ts_boxplots.png", plot = g2)
#rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
#gc() #garbage collection
```
```{r fig ts and bp for paper}
g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/ts_ts_boxplots.png", plot = g)
rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
gc() #garbage collection
```
